Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-07-25 GWLDCI.tex
finished read through

This proof is by a symmetrical construction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough}

Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ and $f$ be as above.  Then $f$ must have two vertices strictly on each side of $d$: name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).  Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.

@@

    Since $\tau(W)$ and $\tau(X)$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $\tau(W)$ that crosses through a non-triangle face $f$ of $\tau(X)$. 
    It will be most convenient to consider faces in terms of their normal vectors. We make use of the construction discussed on p8 of \cite{CSZinequivalent}: namely, pick one side of $d$ to be positive and define the $i$th coordinate of the vector $\omega^+_d$ to be
    \[
    \omega^+_d(i) = \begin{cases} \text{dist}(x_i, d) & \text{if $x$ is on the positive side of $d$}\\ 0 & \text{otherwise} \end{cases}
    \]
    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal; however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.  The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is \[\textstyle\frac{1}{2}(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2).\]

>>>>

This proof is by a symmetrical construction, where we give a proof with respect to a single edge in the face $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough} \sanote{agreed. Withdraw previous questions}

Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face, $f$, of $D_2$. Then $f$ must have two vertices strictly on each side of $d$: name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).  Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.

@@

    Since $\tau(W)$ and $\tau(X)$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $\tau(W)$ that crosses through a non-triangle face $f$ of $\tau(X)$. 
    It will be most convenient to consider faces in terms of their normal vectors. We make use of the construction discussed on page 8 of \cite{CSZinequivalent}: namely, pick one side of $d$ to be positive and define the $i$th coordinate of the vector $\omega^+_d$ to be
    \[
    \omega^+_d(i) = \begin{cases} \text{dist}(x_i, d) & \text{if $x$ is on the positive side of $d$}\\ 0 & \text{otherwise} \end{cases}
    \]
    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal; however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.  The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is \[\textstyle\frac{1}{2}(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2).\]
